Ouflows and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy

### 2017-02-23 paper/letter.tex
model selection

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Atypical Dwarf LAE]{
Lyman-$\alpha$ emission line outlines a massive dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

@@

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
Ouflows and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
\author[J.E. Forero-Romero et al.]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Max Gronke$^2$, 
Mar\'ia Camila Remolina-Guti\'errez$^1$,
\newauthor
Nicol\'as Garavito-Camargo$^3$, 
Mark Dijkstra$^2$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
$^2$ Institute of Theoretical Astrophysics, University of Oslo,
Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
Avenue, Tucson, AZ 85721, USA. 
}

@@

We compare each resulting spectra to the observational results from
\tol\ after normalizing the observed and simulated spectra to have a a
flux integral of one.
We then build a $\chi^2$ on the normalized flux measurements for each one
of the $2500$ models, and then select for further analysis the best
$1\%$ models according to the lowest $\chi^2$ values.
These best $50$ models have a large span in $\chi^2$ going from values
of $1000$ to $3000$.

@@

In this paper we presented two theoretical models that explain the main
observational feature of \tol, which have been unexplained so far.
One model is based on a multiphase ISM and the other on gas rotation,  
It is the first time that an observed \lya\ profile can be fully
reproduced by either of these two conditions.
Furthermore, the kinematics of both models suggest a dynamical mass
ten times larger than the baryonic mass infered from observations.
